Untitled Draft

### 2023-04-13 doc/manuscript.Rmd
Automate docs
Co-authored-by: James Conigrave <12742211+conig@users.noreply.github.com>

Should prevent the cases where the images are being renamed
and not matching the files.

```{r load-targets, include=FALSE}
tar_load(model_list_by_age)
tar_load(data_clean)
tar_load(purdy_pictures_by_age)
tar_load(model_tables_age)
tar_load(demog_table)
pretty <- function(x) format(x, big.mark = ",")

@@

```{r}
n_participants <- length(unique(data_clean$participant_id))
weekday_table <- (data_clean$weekday_x) |> table()
weekday <- chisq.test(weekday_table)
weekday_res <-glue::glue("$\\chi^2_{(..weekday$parameter..)}$ = ..papaja::print_num(weekday$statistic).., p = ..papaja::print_p(weekday$p.value)..", .open = "..", .close = "..")

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models
We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
There was no meaningful relationship between physical activity volume and sleep duration.
However, we observed a curvilinear relationships between physical activity volume and sleep efficiency, onset, and regularity, all of which interacted with age.
Sleep efficiency improved with greater physical activity volume, but improvements tapered off for older individuals.
Physical activity volume and sleep onset had a positive association for younger individuals, but a negative association for older individuals, where sleep onset was reduced among those with the highest physical activity.
There was a strong positive association between physical activity volume and sleep regularity, which was strongest among older participants.
For participants aged 35 years and above, this link weakened among those with a physical activity volume greater than two standard deviations.

```{r sleep-outcomes}
papaja::apa_table(
  model_tables_age$sleep$data,
  caption = model_tables_age$sleep$caption,
  note = model_tables_age$sleep$note,
  col_spanners = model_tables_age$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on physical activity volume. The panels on the left show the curvilinear relationship between PA volume and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero. These plots demonstrate exact turning points where the effects of PA volume change by age."}
knitr::include_graphics(here::here("Figures/sleep on pa_volume by Age.jpg"), error = FALSE)
```

@@

```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on physical activity intensity. The panels on the left show the curvilinear relationship between PA intensity and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here("Figures/sleep on pa_intensity by Age.jpg"), error = FALSE)
```

@@

```{r pa-outcomes}
papaja::apa_table(
  model_tables_age$physical_activity$data,
  caption = model_tables_age$physical_activity$caption,
  note = model_tables_age$physical_activity$note,
  col_spanners = model_tables_age$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration. The panels on the left show the curvilinear relationship between sleep duration and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here("Figures/PA on sleep_duration_lag by Age.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency. The panels on the left show the curvilinear relationship between sleep efficiency and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here("Figures/PA on sleep_efficiency_lag by Age.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset. The panels on the left show the curvilinear relationship between sleep onset and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here("Figures/PA on sleep_onset_lag by Age.jpg"), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity. The panels on the left show the curvilinear relationship between sleep regularity and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here("Figures/PA on sleep_regularity_lag by Age.jpg"), error = FALSE)
```

>>>>

```{r load-targets, include=FALSE}
tar_load(data_clean)
tar_load(purdy_pictures_by_age)
tar_load(model_tables_by_age)
tar_load(demog_table)
pretty <- function(x) format(x, big.mark = ",")

@@

```{r}
n_participants <- length(unique(data_clean$participant_id))
weekday_table <- (data_clean$weekday) |> table()
weekday <- chisq.test(weekday_table)
weekday_res <-glue::glue("$\\chi^2_{(..weekday$parameter..)}$ = ..papaja::print_num(weekday$statistic).., p = ..papaja::print_p(weekday$p.value)..", .open = "..", .close = "..")

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes) and Figure \@ref(fig:sleep-by-volume-fig)
There was no meaningful relationship between physical activity volume and sleep duration.
However, we observed a curvilinear relationships between physical activity volume and sleep efficiency, onset, and regularity, all of which interacted with age.
Sleep efficiency improved with greater physical activity volume, but improvements tapered off for older individuals.
Physical activity volume and sleep onset had a positive association for younger individuals, but a negative association for older individuals, where sleep onset was reduced among those with the highest physical activity.
There was a strong positive association between physical activity volume and sleep regularity, which was strongest among older participants.
For participants aged 35 years and above, this link weakened among those with a physical activity volume greater than two standard deviations.

```{r sleep-outcomes}
papaja::apa_table(
  model_tables_by_age$sleep$data,
  caption = model_tables_by_age$sleep$caption,
  note = model_tables_by_age$sleep$note,
  col_spanners = model_tables_by_age$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig, fig.cap = "Sleep metrics on physical activity volume. The panels on the left show the curvilinear relationship between PA volume and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero. These plots demonstrate exact turning points where the effects of PA volume change by age."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_pa_volume), error = FALSE)
```

@@

```{r sleep-by-intensity-fig, fig.cap = "Sleep metrics on physical activity intensity. The panels on the left show the curvilinear relationship between PA intensity and each of the sleep outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_pa_intensity), error = FALSE)
```

@@

```{r pa-outcomes}
papaja::apa_table(
  model_tables_by_age$physical_activity$data,
  caption = model_tables_by_age$physical_activity$caption,
  note = model_tables_by_age$physical_activity$note,
  col_spanners = model_tables_by_age$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig, fig.cap = "Physical activity by sleep duration. The panels on the left show the curvilinear relationship between sleep duration and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_duration_lag), error = FALSE)
```

@@

```{r PA-by-sleep-efficiency-fig, fig.cap = "Physical activity by sleep efficiency. The panels on the left show the curvilinear relationship between sleep efficiency and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_efficiency_lag), error = FALSE)
```

@@

```{r PA-by-sleep-onset-fig, fig.cap = "Physical activity by sleep onset. The panels on the left show the curvilinear relationship between sleep onset and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_onset_lag), error = FALSE)
```

@@

```{r PA-by-sleep-regularity-fig, fig.cap = "Physical activity by sleep regularity. The panels on the left show the curvilinear relationship between sleep regularity and each of the physical activity outcomes at the ages indicated in each column. The panels on the right show the same relationships but by age continuously. The white band indicates predictions which were not significantly different from zero."}
knitr::include_graphics(here::here(purdy_pictures_by_age$predictor_sleep_regularity_lag), error = FALSE)
```
